---
title: <br><br><center>GUIDE AND FREELANCE RATES <center>
author: "Oliver Martinez"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 

```{r knitr_init, echo=FALSE, cache=FALSE, message= FALSE,warning=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=750)
```


```{r echo=FALSE, message=FALSE,warning=FALSE}
library(readxl)
library(dplyr)
library(knitr)
library(kableExtra)
```


## **COMUNITAT VALENCIANA** {.tabset .tabset-fade .tabset-pills}

### ALICANTE

### VALENCIA

## **CATALUNYA** {.tabset .tabset-fade .tabset-pills}

### BARCELONA

<br>

```{r echo=FALSE, message=FALSE,warning=FALSE}

guides <- read_excel("vendorprices.xlsx", sheet = "GUIDES")
bcnguides <- guides[guides$CITY == "BCN",]
bcnguides[is.na(bcnguides)] <- " "
bcnguides$RATE <- paste('€',formatC(bcnguides$RATE, big.mark=','))

bcnguides %>% select(NAME,1,3:ncol(bcnguides)) %>% kable(escape = T) %>% 
kable_styling(bootstrap_options = c("striped","condensed","hover"), full_width = T, fixed_thead = T) %>% 
  row_spec(0, bold = T, background = "#FF8000", color = "white")

```


### GIRONA

## **CENTRO** {.tabset .tabset-fade .tabset-pills}

### MADRID

### SALAMANCA

## **ANDALUSIA** {.tabset .tabset-fade .tabset-pills}

### MALAGA

### GRANADA

<br>

```{r echo=FALSE, message=FALSE,warning=FALSE}

guides <- read_excel("vendorprices.xlsx", sheet = "GUIDES")
graguides <- guides[guides$CITY == "GRA",]
graguides[is.na(graguides)] <- " "
graguides$RATE <- paste('€',formatC(graguides$RATE, big.mark=','))

graguides %>% select(NAME,1,3:ncol(graguides)) %>% kable(escape = T) %>% 
kable_styling(bootstrap_options = c("striped","condensed","hover"), full_width = T, fixed_thead = T) %>% 
  row_spec(0, bold = T, background = "#FF8000", color = "white")

```

### CORDOBA

## **PORTUGAL** {.tabset .tabset-fade .tabset-pills}

### LISBOA

### PORTO
